Model-based pretreatment for regression with correlated variables.

### 2014-04-08 www/article13.tex
update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@508 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

		Variables in $\boldsymbol{X_1}$ are supposed to be independent.
	%Thus if one have some hypothesis on the distribution of some variables (exponentially distributed for example) it is possible to use it without impacting the model in other ways. %compute corresponding $\psi$ according to it. %and then improve the walk (will keep a structure only if it is really relevant).%and give it as an input of \textsc{CorReg} and then improve the efficiency of the algorithm (it will find a structure only if it is really relevant).
	We now have a full generative model.
	\subsection{Penalization of the integrated likelihood} \label{compstruct}
  To obtain the marginal regression model we need $S$, the linear structure between the covariates.
  Cross-validation is very time-consuming and thus not friendly with combinatory problematics. Moreover, we need a criterion compatible with structures of different sizes (varying $p_2$) and not related with $Y$ because the structure is inherent to $\boldsymbol{X}$ only. Thus it must be a global criterion. 	
	Our full generative generative model allows us to compare structures with criterions like the Bayesian Information Criterion ($BIC$) which penalize the log-likelihood of the joint law on $\boldsymbol{X}$ according to the complexity of the structure~\cite{BIChuard}.

	We note $\boldsymbol{\Theta}$ the set of the parameters of the generative model
	\begin{eqnarray}
		P(S|\boldsymbol{X})&\propto& P(\boldsymbol{X}|S)P(S) \label{approxBIC}\\
		-2\log P(\boldsymbol{X}|S)&\approx & BIC=-2\mathcal{L}(\boldsymbol{X},S,\boldsymbol{\Theta})+|\boldsymbol{\Theta}|\log(n)\\  
	\end{eqnarray}
	But $BIC$ tends to give too complex structures because we test a great range of models. 
	Thus we choose to penalise the complexity a bit more with a hierarchical uniform {\it a priori} law $P(S)=P(I_1 | p_1,I_2,p_2)P(p_1|I_2,p_2)P(I_2|p_2)P(p_2)$  instead of a simple uniform law on $S$.
%	 Thus we have :
%		\begin{eqnarray}
%		BIC^*(X|S)&=&BIC(X|S) +\ln(P(S)) \label{Bicstar}
%	\end{eqnarray}		
	It increases penalty on complexity for $p_2<\frac{p}{2}$ and $p_1^j<\frac{p}{2}$ . Hence %when using $BIC*$ 
	this constraint on $\hat{p}_2$ and $\hat{p}_1^j$ is made in the MCMC in the followings.
		We do not change $BIC$ but only $P(S)$ so the properties are the same as classical $BIC$ but we will obtain better results when our hypothesis is verified.

@@

 \subsubsection{Initialisation(s)}

 If we have some knowledge about some sub-regressions (physical models for example) we can add them in the found and/or initial structure. So the model is really expert-friendly.
The initial structure can be based on a first warming algorithm taking the correlations into account. coefficients are randomly placed into $I_1$, weighted by the absolute value of the correlations. We do so in the followings. Then this structure could be for example reduced by the hadamard product with the binary matrix obtained by Graphical Lasso\cite{friedman2008sparse} that makes selection in the precision matrix but it is time consuming.

>>>>

		Variables in $\boldsymbol{X_1}$ are supposed to be independent.
	%Thus if one have some hypothesis on the distribution of some variables (exponentially distributed for example) it is possible to use it without impacting the model in other ways. %compute corresponding $\psi$ according to it. %and then improve the walk (will keep a structure only if it is really relevant).%and give it as an input of \textsc{CorReg} and then improve the efficiency of the algorithm (it will find a structure only if it is really relevant).
	We now have a full generative model.
	\subsection{Penalization of the integrated likelihood} \label{compstruct}
  To obtain the marginal regression model we need $S$, the linear structure between the covariates.
  Cross-validation is very time-consuming and thus not friendly with combinatory problematics. Moreover, we need a criterion compatible with structures of different sizes (varying $p_2$) and not related with $Y$ because the structure is inherent to $\boldsymbol{X}$ only. Thus it must be a global criterion. 	
	Because it is about model selection and we are able to provide a full generative model, we decide to follow a Bayesian approach (\cite{raftery1995bayesian}, \cite{andrieu1999joint},\cite{chipman2001practical}).  
	Our full generative generative model allows us to compare structures with criterions like the Bayesian Information Criterion ($BIC$) which penalize the log-likelihood of the joint law on $\boldsymbol{X}$ according to the complexity of the structure~\cite{BIChuard}.

	We note $\boldsymbol{\Theta}$ the set of the parameters of the generative model
	\begin{eqnarray}
		P(S|\boldsymbol{X})&\propto& P(\boldsymbol{X}|S)P(S) \label{approxBIC}\\
		-2\log P(\boldsymbol{X}|S)&\approx & BIC=-2\mathcal{L}(\boldsymbol{X},S,\boldsymbol{\Theta})+|\boldsymbol{\Theta}|\log(n)  
	\end{eqnarray}
	But $BIC$ tends to give too complex structures because we test a great range of models. 
	Thus we choose to penalise the complexity a bit more with a hierarchical uniform {\it a priori} law $P(S)=P(I_1 | p_1,I_2,p_2)P(p_1|I_2,p_2)P(I_2|p_2)P(p_2)$  instead of a simple uniform law on $S$.
%	 Thus we have :
%		\begin{eqnarray}
%		BIC^*(X|S)&=&BIC(X|S) +\ln(P(S)) \label{Bicstar}
%	\end{eqnarray}		
	It increases penalty on complexity for $p_2<\frac{p}{2}$ and $p_1^j<\frac{p}{2}$ . Hence %when using $BIC*$ 
	this constraint on $\hat{p}_2$ and $\hat{p}_1^j$ is made in the MCMC in the followings.
		We do not change $BIC$ but only $P(S)$ so the properties are the same as classical $BIC$ but we will obtain better results when our hypothesis is verified.

@@

 \subsubsection{Initialisation(s)}
 If we have some knowledge about some sub-regressions (physical models for example) we can add them in the found and/or initial structure. So the model is really expert-friendly.
The initial structure can be based on a first warming algorithm taking the correlations into account. coefficients are randomly placed into $I_1$, weighted by the absolute value of the correlations. We do so in the followings. Then this structure could be for example reduced by the hadamard product with the binary matrix obtained by Graphical Lasso\cite{friedman2008sparse} that makes selection in the precision matrix but it is time consuming.
